### 2017-05-13 paper/evaluation.tex
anotacao de problema do maven
pass on rq7 (not done); going back to rq6

\subsection{Tradeoffs}
\label{sec:rq6-tradeoffs}
\Jbc{Check $\rightarrow$}
This dimension assesses the impact of using distinct parallel
configurations on test flakiness (negative impact) and speedup We are
interested in understanding how efficiency (\ie, testing cost) and
flakiness (\ie, failing tests) are affected when we run a test suite
with different parallel configurations.  Recall that increased
resource contention obtained with parallelism can lead to concurrency
issues such as data races.  Flakiness and speedup are contradictory
forces that drive configuration selection.  (positive impact).
Furthermore, note that Section~\ref{sec:rqD} evaluated speedup in
isolation, focused on projects configured to use parallelism by
default.

@@

To answer this research question, we ran ten different subjects
against all configurations described in Section~\ref{sec:modes} and
compared their running times and rate of test flakiness.  We used the
sequential execution (configuration \emph{\Seq{}}) associated with
each project as the comparison baseline in this experiment.  We
selected subjects from the medium and long groups from
Section~\ref{sec:rqA} and further selected their longest test module
for testing.  The rationale is to obtain a diverse set of subjects
exposing a wide range of running times (range observed 1.1m-8.2m) and
number of test cases (range observed 54-17,513) and yet be able to run
the experiment in reasonable time.  We ran each project on each
configuration with ten seeds.  Overall, we needed to reran test suites
600 times, 60 times (10x6 configurations) on each project.  Given the
low standard deviations observed in our measurements we consider ten
seeds reasonable for this experiment.

@@

\Mar{...estou aqui...}

In a first attempt of this experiment, we considered using Maven to
run the subjects on the different parallel configurations. However, we
noticed that some executions using parallelism within a JVM did not
reflect the desired behavior although we carefully verified the
library versions from the subjects tested to avoid compatibility
issues.
To make the experiment viable and obtain the parallel configurations,
we implemented a script and a JUnit runner to emulate the effect of
parallel configurations from Maven Surefire.
Our script takes a list o tests classes to run as an input and outputs
the results (\ie, number of test methods, failures, skips, and elapsed
time) for each parallel configuration. Initially, we use an existing
Maven log to identify the test classes to run, and we use the Maven
dependency plugin~\cite{maven-dep} to build the project's classpath with
the command \CodeIn{mvn dependency:build-classpath}. Once we have the
classpath and the tests to run, we invoke our JUnit runner that runs
the test classes with different parallel configurations at once. For
the sequential execution, we ivonke the default JUnit test runner. For
parallelism within a JVM (\ie, the configurations \SeqClassParMeth{},
\ParClassSeqMeth{}, and \ParClassParMeth{}), we configured the JUnit
runner with ParallelComputer~\cite{junit-parallel} that internally uses a pool of
threads with cache to run test classes and methods. For the
configurations with forked JVMs (\ie, \ForkSeq{} and \ForkParMeth{}),
we have a queue of test classes and a pool of three threads that
``consumes'' the next test class and spawns a JVM to run it.
Recall that in our setup (see Section~\ref{sec:setup}), we limited our
kernel to use only three cores and reserved one for OS-related
processes.
To verify that our approach satisfies the purpose of this experiment,
we executed some subjects on Maven and compared the performance with
our artifacts and observed nonsignificant differences (a fraction of
seconds in most cases).
\Comment{
    To obtain parallel configurations, we implemented a script that
    takes a subject and a configuration label as inputs (\eg
    \CodeIn{mapdb "c0"}), and the script outputs the modified version
    of the subject with the desired configuration. The workflow
    consists in copying the project directory to a new directory,
    finding all existing build files (\ie, \pomf{} files), and
    modifying all existing Maven Surefire configurations with new
    values for the parameters \CodeIn{parallel}, \CodeIn{forkCount},
    and \CodeIn{threadCount} using an XPath~\cite{xpath} library to
    manipulate XML documents. For configurations with forked JVMs
    enabled (\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
    \CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per
    core).  To adjust the pool of threads for parallelism within a
    JVM, we changed the parameter \CodeIn{threadCount} with
    \Jbc{should we consider 2 as it is the number of native threads
    per core OR 6 as it represents 3 Cores * 2 native threads?}.To run
    the subjects and their respective variations (\ie, the modified
    versions according to the parallelism configuration), we used a
    similar approach as described in Figure~\ref{fig:mvn-execution}
    except that...
}
Also, we used the \CodeIn{timeout} command~\cite{timeout-cmd} in our
scripts to monitor the execution, and we configured the command to
dispatch a \emph{kill} signal if the test execution exceeds a given
time limit. We imposed this time constraint to avoid hanging
indefinitely the experiment execution due to some thread contention
that may occur (\eg, deadlock or livelock).  Finally, we saved each
execution log and stack traces generated outputed from JUnit to
collect the execution time, the number of failing tests, and for
reference to analyze and diagnose outliers in our results.  For
efficiency, we reported the speedup (\ie, $T_{\text{s}} /
T_{\text{p}}$), and for flakiness, we reported the rate of failing
tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).
Figure~\ref{tab:rq6-table} summarizes the obtained results ordered by
subject's name. Values are reported in average \Fix{LEMBRAR DE MOSTRAR
VALORES DE DESVIO PADRAO!}.

@@

\Fix{Draw conclusions}

>>>>

\subsection{Tradeoffs}
\label{sec:rq6-tradeoffs}

%%  We are
%% interested in understanding how efficiency (\ie, testing cost) and
%% flakiness (\ie, failing tests) are affected when we run a test suite
%% with different parallel configurations.

This dimension assesses the impact of using distinct parallel
configurations on test flakiness and speedup.  Recall that increased
resource contention obtained with parallelism can lead to concurrency
issues such as data races that could interfere in results of dependent
tests~\cite{luo-etal-fse2014,bell-etal-esecfse2015}.  Flakiness and
speedup are contradictory forces that drive configuration selection.
Note that Section~\ref{sec:rqD} evaluated speedup in isolation.

@@

To answer this research question, we selected ten different subjects,
ran their test suites against all configurations described in
Section~\ref{sec:modes}, and compared their running times and rate of
test flakiness.  We used the sequential execution (configuration
\emph{\Seq{}}) associated with each project as the comparison baseline
in this experiment.  We selected subjects from the medium and long
groups from Section~\ref{sec:rqA} and further selected their longest
test module for testing.  The rationale for this selection was to
obtain a diverse set of subjects exposing a wide range of running
times (range observed 1.1m-8.2m) and number of test cases (range
observed 54-17,513) and yet be able to run the experiment in
reasonable time.  We ran each project on each configuration with ten
seeds.  Overall, we needed to reran test suites 600 times, 60 times
(10x6 configurations) on each project.  Given the low standard
deviations observed in our measurements we consider ten seeds
reasonable for this experiment.

@@

%% In a first attempt of this experiment, we considered using Maven to
%% run the subjects on the different parallel configurations. However,

\noindent\textbf{JUnit.} It is worth mentioning that we used JUnit as
opposed to Maven to run configurations \emph{C*}.  After carefully
verifying library versions for compatibility issues and comparing
results with JUnit's we observed that several of Maven's executions
exposed problems (\eg{} timeouts).  These issues are documented in our
website~\cite{ourwebpage} through Docker containers.  To address those
issues we implemented basic JUnit runner reflecting the effects of
parallel configurations from Maven Surefire.

\Mar{estou aqui...}

Our script takes a list
o tests classes to run as an input and outputs the results (\ie,
number of test methods, failures, skips, and elapsed time) for each
parallel configuration. Initially, we use an existing Maven log to
identify the test classes to run, and we use the Maven dependency
plugin~\cite{maven-dep} to build the project's classpath with the
command \CodeIn{mvn dependency:build-classpath}. Once we have the
classpath and the tests to run, we invoke our JUnit runner that runs
the test classes with different parallel configurations at once. For
the sequential execution, we ivonke the default JUnit test runner. For
parallelism within a JVM (\ie, the configurations \SeqClassParMeth{},
\ParClassSeqMeth{}, and \ParClassParMeth{}), we configured the JUnit
runner with ParallelComputer~\cite{junit-parallel} that internally
uses a pool of threads with cache to run test classes and methods. For
the configurations with forked JVMs (\ie, \ForkSeq{} and
\ForkParMeth{}), we have a queue of test classes and a pool of three
threads that ``consumes'' the next test class and spawns a JVM to run
it.  Recall that in our setup (see Section~\ref{sec:setup}), we
limited our kernel to use only three cores and reserved one for
OS-related processes.  To verify that our approach satisfies the
purpose of this experiment, we executed some subjects on Maven and
compared the performance with our artifacts and observed
nonsignificant differences (a fraction of seconds in most cases).
\Comment{ To obtain parallel configurations, we implemented a script
  that takes a subject and a configuration label as inputs (\eg
  \CodeIn{mapdb "c0"}), and the script outputs the modified version of
  the subject with the desired configuration. The workflow consists in
  copying the project directory to a new directory, finding all
  existing build files (\ie, \pomf{} files), and modifying all
  existing Maven Surefire configurations with new values for the
  parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
  \CodeIn{threadCount} using an XPath~\cite{xpath} library to
  manipulate XML documents. For configurations with forked JVMs
  enabled (\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
  \CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per
  core).  To adjust the pool of threads for parallelism within a JVM,
  we changed the parameter \CodeIn{threadCount} with \Jbc{should we
    consider 2 as it is the number of native threads per core OR 6 as
    it represents 3 Cores * 2 native threads?}.To run the subjects and
  their respective variations (\ie, the modified versions according to
  the parallelism configuration), we used a similar approach as
  described in Figure~\ref{fig:mvn-execution} except that...  } Also,
we used the \CodeIn{timeout} command~\cite{timeout-cmd} in our scripts
to monitor the execution, and we configured the command to dispatch a
\emph{kill} signal if the test execution exceeds a given time
limit. We imposed this time constraint to avoid hanging indefinitely
the experiment execution due to some thread contention that may occur
(\eg, deadlock or livelock).  Finally, we saved each execution log and
stack traces generated outputed from JUnit to collect the execution
time, the number of failing tests, and for reference to analyze and
diagnose outliers in our results.

For
efficiency, we reported the speedup (\ie, $T_{\text{s}} /
T_{\text{p}}$), and for flakiness, we reported the rate of failing
tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).
Figure~\ref{tab:rq6-table} summarizes the obtained results ordered by
subject's name. Values are reported in average \Fix{LEMBRAR DE MOSTRAR
VALORES DE DESVIO PADRAO!}.

@@

\Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de
jvm - maven surefire nao tratava algumas exceptions que aconteciam na
execucao do teste, (3) timeout}

### 2017-05-13 paper/threats.tex
pass on rq7 (not done); going back to rq6

The main threats to validity of this study are the following.
\textit{External Validity:} Generalization of our findings is limited
to our selection of subjects, testing framework, and build system.  To
mitigate that issue, we selected subjects according to an objective
criteria, described in Section~\ref{sec:subjects}.  It remains to
evaluate the extent to which our observations would change when using
different testing frameworks and build systems.  \textit{Internal
  Validity:} Our results could be influenced by unintentional mistakes
made by humans who interpreted survey data and implemented scripts to
collect and analyze data. All those tasks could introduce bias.  To
mitigate those threats, we worked in pairs as to increase chances of
capturing unintentional mistakes.  \textit{Construct Validity:} We
considered a number of metrics in this study that could influence some
of our interpretations.  For example, we measured number of test cases
per suite, distribution of test costs in a suite, time to run a suite,
etc.  In principle, these metrics may not reflect the main problems
associated with test efficiency.\Mar{...elaborate...}

>>>>

The main threats to validity of this study are the following.
\textit{External Validity:} Generalization of our findings is limited
to our selection of subjects, testing framework, and build system.  To
mitigate that issue, we selected subjects according to an objective
criteria, described in Section~\ref{sec:subjects}.  It remains to
evaluate the extent to which our observations would change when using
different testing frameworks and build systems.  \textit{Internal
  Validity:} Our results could be influenced by unintentional mistakes
made by humans who interpreted survey data and implemented scripts and
code to collect and analyze data. For example, we developed JUnit
runners to reproduce Maven's parallel configurations.  All those tasks
could introduce bias.  To mitigate those threats, we worked in pairs
as to increase chances of capturing unintentional mistakes.
\textit{Construct Validity:} We considered a number of metrics in this
study that could influence some of our interpretations.  For example,
we measured number of test cases per suite, distribution of test costs
in a suite, time to run a suite, etc.  In principle, these metrics may
not reflect the main problems associated with test
efficiency.\Mar{...elaborate...}
